---
title: "Petrol Analysis"
author: "Joseph Barrett"
date: '2022-11-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lawstat)
library(EnvStats)
library(TeachingDemos)
library(dplyr)
library(tidyr)
library(fitdistrplus)
library(Hmisc)
```

# Analysis of Petrol Data Collection

```{r}
data <- read.csv("Data Collection_seconds.csv")
df = data.frame(data)
```

```{r}
unique(df$Type.of.Customer..Wait.to.see.where.they.go.)
```


```{r}
# describe(data)
summary(data)
```
## Testing for Total Time on Property 
```{r}
shapiro.test(data$Total.Time.on.Property)
```
Hence, we cannot assume normality. 

Our samples are independent, so we now test for symetricity. 

```{r}
symmetry.test(data$Total.Time.on.Property)
```


```{r}
na.omit(data$Total.Time.on.Property)
print(data$Total.Time.on.Property)
```

# Filtering to find distribution of each input by time in QUEUE

## pump only

```{r}
pump <- filter(df, df$Type.of.Customer..Wait.to.see.where.they.go.=="Pump Only")
pump_queue_time <- pump$Time.spent.in.Queue
#pump_total_time
descdist(pump$Time.spent.in.Queue, discrete = FALSE)

pump_dist <- fitdist(pump_queue_time, "exp")
summary(pump_dist)
plot(pump_dist)
```
## Pump and Store

```{r}
store_and_pump <- filter(df, df$Type.of.Customer..Wait.to.see.where.they.go.=="Store and Pump")
store_pump_queue_time <- store_and_pump$Time.spent.in.Queue
#store_pump_total_time

descdist(store_pump_queue_time, discrete = FALSE)
store_and_pump_dist <- fitdist(store_pump_queue_time, "exp")

summary(store_and_pump_dist)
plot(store_and_pump_dist)
```


## Store only
Not enough data, assume normal distribution. 

## Time at pump for store and pump only
```{r}


store_and_pump <- filter(df, df$Type.of.Customer..Wait.to.see.where.they.go.=="Store and Pump")
store_and_pump
store_pump_pump_time <- store_and_pump$Time.Spent.At.the.Pump..0.if.not.at.the.pump.at.all.

descdist(store_pump_pump_time, discrete = FALSE)
store_and_pump_gas_dist <- fitdist(store_pump_pump_time, "gamma")

summary(store_and_pump_gas_dist)
plot(store_and_pump_gas_dist)


```

```{r}
1073798*.23
```


# Filtering to find distribution of each input, by total time
## pump only

```{r}
pump <- filter(df, df$Type.of.Customer..Wait.to.see.where.they.go.=="Pump Only")
pump_total_time <- pump$Total.Time.on.Property
descdist(pump$Total.Time.on.Property, discrete = FALSE)
pump_dist <- fitdist(pump_total_time, "gamma")
summary(pump_dist)
plot(pump_dist)
```
```{r}
1/0.02584788
```

## Pump and Store

```{r}
store_and_pump <- filter(df, df$Type.of.Customer..Wait.to.see.where.they.go.=="Store and Pump")
store_pump_total_time <- store_and_pump$Total.Time.on.Property

descdist(store_pump_total_time, discrete = FALSE)
store_and_pump_dist <- fitdist(store_pump_total_time, "unif")

summary(store_and_pump_dist)
plot(store_and_pump_dist)
```

